Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-05-06 paper.tex
Interpolate --> extrapolate
Use gmail since UNH address changing
Add NS type to table

\author{Peter Bachant}
\email[]{pxl3@unh.edu}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Center for Ocean Renewable Energy, University of New Hampshire,
Durham, NH}

@@

\begin{abstract}
    The near-wake of a vertical-axis cross-flow turbine (CFT) was modeled
    numerically via blade-resolved $k$--$\omega$ SST and Spalart--Allmaras RANS
    models in two and three dimensions. Results for each case are compared with
    experimental measurements of the turbine shaft power, overall drag, mean
    velocity, turbulence kinetic energy, and momentum transport terms in the
    near-wake at one diameter downstream. It was shown that 2-D simulations
    overpredict turbine loading and do not resolve mean vertical momentum
    transport, which plays an important role in the near-wake's momentum
    balance. The 3-D simulations fared better at predicting performance, with
    the Spalart--Allmaras model predictions being closest to the experiments.
    The SST model more accurately predicted the turbulence kinetic energy while
    the Spalart--Allmaras model more closely matched the momentum transport
    terms in the near-wake. These results show the potential of blade-resolved
    RANS as a design tool and a way to ``interpolate'' experimental flow field
    measurements.
\end{abstract}

@@

\begin{table}
    \centering
    \begin{tabular}{c|c|c|c}
        Author & Turbulence modeling & Perf. val. & Wake val. \\
        \hline
        Alaimo et al.~\cite{Alaimo2015} & $k$--$\epsilon$ & N/A & N/A \\
        Marsh et al.~\cite{Marsh2015} & SST & Reference~\cite{Rawlings2008} & N/A \\
        Orlandi et al.~\cite{Orlandi2015} & SST & References~\cite{Akins1989,Mertens2003} & N/A \\
        Lam \& Peng~\cite{Lam2016} & SST RANS \& IDDES & N/A & Reference~\cite{Tescione2014} \\
        Nini et al.~\cite{Nini2014} & Spalart--Allmaras & N/A & Reference~\cite{Battisti2011} \\
        Boudreau \& Dumas~\cite{Boudreau2015} & DDES & N/A & N/A \\
        Li et al.~\cite{Li2013} & SST \& Smagorinsky--Lilly LES & Reference~\cite{McLaren2011} & N/A \\
        Howell et al.~\cite{Howell2010} & $k$--$\epsilon$ RNG & Reference~\cite{Howell2010} & N/A
    \end{tabular}

>>>>

\author{Peter Bachant}
\email[]{pete.bachant@gmail.com}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Center for Ocean Renewable Energy, University of New Hampshire,
Durham, NH}

@@

\begin{abstract}
    The near-wake of a vertical-axis cross-flow turbine (CFT) was modeled
    numerically via blade-resolved $k$--$\omega$ SST and Spalart--Allmaras RANS
    models in two and three dimensions. Results for each case are compared with
    experimental measurements of the turbine shaft power, overall drag, mean
    velocity, turbulence kinetic energy, and momentum transport terms in the
    near-wake at one diameter downstream. It was shown that 2-D simulations
    overpredict turbine loading and do not resolve mean vertical momentum
    transport, which plays an important role in the near-wake's momentum
    balance. The 3-D simulations fared better at predicting performance, with
    the Spalart--Allmaras model predictions being closest to the experiments.
    The SST model more accurately predicted the turbulence kinetic energy while
    the Spalart--Allmaras model more closely matched the momentum transport
    terms in the near-wake. These results show the potential of blade-resolved
    RANS as a design tool and a way to ``extrapolate'' experimental flow field
    measurements.
\end{abstract}

@@

\begin{table}
    \centering
    \begin{tabular}{c|c|c|c}
        Author & Turbulence modeling & Perf. val. & Wake val. \\
        \hline
        Alaimo et al.~\cite{Alaimo2015} & $k$--$\epsilon$ RANS & N/A & N/A \\
        Marsh et al.~\cite{Marsh2015} & SST RANS & Reference~\cite{Rawlings2008} & N/A \\
        Orlandi et al.~\cite{Orlandi2015} & SST RANS & References~\cite{Akins1989,Mertens2003} & N/A \\
        Lam \& Peng~\cite{Lam2016} & SST RANS \& IDDES & N/A & Reference~\cite{Tescione2014} \\
        Nini et al.~\cite{Nini2014} & Spalart--Allmaras RANS & N/A & Reference~\cite{Battisti2011} \\
        Boudreau \& Dumas~\cite{Boudreau2015} & Spalart--Allmaras DDES & N/A & N/A \\
        Li et al.~\cite{Li2013} & SST RANS \& Smagorinsky--Lilly LES & Reference~\cite{McLaren2011} & N/A \\
        Howell et al.~\cite{Howell2010} & $k$--$\epsilon$ RNG RANS & Reference~\cite{Howell2010} & N/A
    \end{tabular}
